---
title: "all data analysis"
author: "Bianca Massacci"
date: "5/31/2024"
output: html_document
---

# Load the libraries

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(reshape2)
library(ggcorrplot)
library(GGally)
```

# Load the data
```{r}
# Specify the path to the Excel file
file_path <- "/Users/bmassacci/main_folder/maastricht/academics/quantum_thesis/scripts/EVOL-WGAN-COMPLETE/output/all_results.xlsx"

# Load the data from the first sheet
all_data <- read_excel(file_path, sheet = 1)

# Display the first few rows of the data to check it
head(all_data)
```

# Preprocessing

```{r}
colnames(all_data)
```


```{r}
print(paste0("Length of fid: ", length(all_data$fid), ". Type of fid: ", typeof(all_data$fid)))
print(paste0("Length of emd_test: ", length(all_data$emd_test_gan), ". Type of e,d_test: ", typeof(all_data$emd_test_gan)))
print(paste0("Length of visual_score: ", length(all_data$visual_score), ". Type of visual_score: ", typeof(all_data$visual_score)))
```

```{r}
unique(all_data$visual_score)
```

```{r}
head(all_data$visual_score, 15)
```

```{r}
# Convert visual_score to numeric values
all_data$visual_score_numeric <- as.numeric(factor(all_data$visual_score, 
                                                   levels = c("very bad", "bad", "medium", "good", "very good"), 
                                                   labels = c(1, 2, 3, 4, 5)))
```

```{r}
head(all_data$visual_score_numeric, 15)
```

Check for NAs:
```{r}
print(paste("FID - number of NAs:", sum(is.na(all_data$fid))))
print(paste("EMD test - number of NAs:", sum(is.na(all_data$emd_test_gan))))
print(paste("Visual Score - number of NAs:", sum(is.na(all_data$visual_score_numeric))))
```

```{r}
all_data %>%
  select(fid, emd_test_gan) %>%
  arrange(fid)
```




Normalize the data:
```{r}
normalize <- function(x) {
  return((x - min(x)) / (max(x) - min(x)))
}

# Force the values between 0 and 1 for each of the evaluation metrics
all_data_clean <- all_data %>%
  mutate(
    visual_score_numeric = normalize(visual_score_numeric),
    fid = normalize(fid),
    emd_test_gan = normalize(emd_test_gan)
  )

```



# Calculate correlations

```{r}
# Calculate Pearson correlation coefficients
pearson_correlation <- cor(all_data_clean[, c("visual_score_numeric", "fid", "emd_test_gan")], use = "complete.obs", method = "pearson")

# Calculate Spearman correlation coefficients
spearman_correlation <- cor(all_data_clean[, c("visual_score_numeric", "fid", "emd_test_gan")], use = "complete.obs", method = "spearman")

# Display the correlation matrices
pearson_correlation
spearman_correlation

```


```{r}
# Function to perform correlation test and extract p-value
correlation_pvalue <- function(x, y, method) {
  test <- cor.test(x, y, method = method)
  return(test$p.value)
}

# Extract the relevant columns
visual_score_numeric <- all_data_clean$visual_score_numeric
fid <- all_data_clean$fid
emd_test_gan <- all_data_clean$emd_test_gan

# Pearson correlation p-values
pearson_p_values <- matrix(NA, nrow = 3, ncol = 3)
rownames(pearson_p_values) <- colnames(pearson_p_values) <- c("visual_score_numeric", "fid", "emd_test_gan")

pearson_p_values[1, 2] <- correlation_pvalue(visual_score_numeric, fid, "pearson")
pearson_p_values[1, 3] <- correlation_pvalue(visual_score_numeric, emd_test_gan, "pearson")
pearson_p_values[2, 3] <- correlation_pvalue(fid, emd_test_gan, "pearson")
pearson_p_values[2, 1] <- pearson_p_values[1, 2]
pearson_p_values[3, 1] <- pearson_p_values[1, 3]
pearson_p_values[3, 2] <- pearson_p_values[2, 3]

# Spearman correlation p-values
spearman_p_values <- matrix(NA, nrow = 3, ncol = 3)
rownames(spearman_p_values) <- colnames(spearman_p_values) <- c("visual_score_numeric", "fid", "emd_test_gan")

spearman_p_values[1, 2] <- correlation_pvalue(visual_score_numeric, fid, "spearman")
spearman_p_values[1, 3] <- correlation_pvalue(visual_score_numeric, emd_test_gan, "spearman")
spearman_p_values[2, 3] <- correlation_pvalue(fid, emd_test_gan, "spearman")
spearman_p_values[2, 1] <- spearman_p_values[1, 2]
spearman_p_values[3, 1] <- spearman_p_values[1, 3]
spearman_p_values[3, 2] <- spearman_p_values[2, 3]

```


# Display the p-values

```{r}
print("Pearson p values:")
pearson_p_values
```

```{r}
print("Spearman p values:")
spearman_p_values
```

# Summary of Findings:
- Visual Score and FID: There is a strong and statistically significant negative correlation.
- Visual Score and EMD Test GAN: There is a strong and statistically significant negative correlation.
- FID and EMD Test GAN: There is a strong and statistically significant positive correlation.

Given these significant correlations, it is clear that FID and EMD metrics are closely related to the visual scores, confirming that FID scores are indicative of the visual quality of the GAN outputs as you initially suspected.


# Plotting

```{r}
# Scatter plot: visual_score_numeric vs fid
ggplot(all_data_clean, aes(x = visual_score_numeric, y = fid)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Scatter Plot: Visual Score vs FID", x = "Visual Score (Numeric)", y = "FID")
```


```{r}
# Scatter plot: visual_score_numeric vs emd_test_gan
ggplot(all_data_clean, aes(x = visual_score_numeric, y = emd_test_gan)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Scatter Plot: Visual Score vs EMD Test GAN", x = "Visual Score (Numeric)", y = "EMD Test GAN")

```


```{r}
# Scatter plot: fid vs emd_test_gan
ggplot(all_data_clean, aes(x = fid, y = emd_test_gan)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Scatter Plot: FID vs EMD Test GAN", x = "FID", y = "EMD Test GAN")

```



```{r}
# Scatter plot: fid vs emd_test_gan
ggplot(all_data, aes(x = fid, y = emd_test_gan)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "FID vs EMD", 
       subtitle = "All experiments",
       x = "FID", y = "EMD") +
  theme(
    plot.title = element_text(size = 18), #face = "bold"
    plot.subtitle = element_text(size = 14),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )


```


```{r}
# Extract the relevant columns
plot_data <- all_data_clean[, c("visual_score_numeric", "fid", "emd_test_gan")]

# Custom function to create 1x3 plot with scatter plots and correlation coefficients
custom_ggpairs <- function(data) {
  # Create empty plot for diagonal
  blank_plot <- ggplot() + theme_void()
  
  # Create individual scatter plots with smooth line
  p1 <- ggplot(data, aes(x = visual_score_numeric, y = fid)) +
    geom_point() +
    geom_smooth(method = "lm", col = "blue") +
    labs(x = "Visual Score (Numeric)", y = "FID")
  
  p2 <- ggplot(data, aes(x = visual_score_numeric, y = emd_test_gan)) +
    geom_point() +
    geom_smooth(method = "lm", col = "blue") +
    labs(x = "Visual Score (Numeric)", y = "EMD Test GAN")
  
  p3 <- ggplot(data, aes(x = fid, y = emd_test_gan)) +
    geom_point() +
    geom_smooth(method = "lm", col = "blue") +
    labs(x = "FID", y = "EMD Test GAN")
  
  # Create a 1x3 plot layout
  gridExtra::grid.arrange(
    p1, p2, p3,
    ncol = 3,
    top = "Pairwise Scatter Plots with Correlations"
  )
}

# Call the custom function with the data
custom_ggpairs(plot_data)

```

```{r}
# Calculate the correlation matrix
cor_matrix <- cor(all_data_clean[, c("visual_score_numeric", "fid", "emd_test_gan")], use = "complete.obs")

# Melt the correlation matrix into a long format
cor_melted <- melt(cor_matrix)

# Create the heatmap
ggplot(cor_melted, aes(x = Var1, y = Var2, fill = abs(value))) +
  geom_tile() +
  scale_fill_gradient2(low = "orange", high = "dark blue", mid = "white",
                       midpoint = 0.6, limit = c(0.2, 1), space = "Lab", 
                       name = "Correlation") +
  geom_text(aes(label = round(abs(value), 2)), color = "black", size = 4) +
  theme_minimal() +
  labs(title = "Correlation Heatmap", x = "", y = "") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```



```{r}
# Box plot: fid grouped by visual_score_numeric
ggplot(all_data, aes(x = as.factor(visual_score_numeric), y = fid)) +
  geom_boxplot() +
  labs(title = "FID vs Visual Score",
       subtitle = "All experiments",
       x = "Visual Score", y = "FID")+
  theme(
    plot.title = element_text(size = 18), #face = "bold"
    plot.subtitle = element_text(size = 14),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )

```


```{r}
# Box plot: emd_test_gan grouped by visual_score_numeric
ggplot(all_data, aes(x = as.factor(round(visual_score_numeric, digits = 1)), y = emd_test_gan)) +
  geom_boxplot() +
  labs(title = "EMD vs visual score",
       subtitle = "All experiments",
       x = "Visual Score", y = "EMD Test GAN") +
  theme(
    plot.title = element_text(size = 18), #face = "bold"
    plot.subtitle = element_text(size = 14),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )
```





```{r}
# Calculate Pearson and Spearman correlations
pearson_corr_fid <- cor.test(all_data_clean$fid, all_data_clean$visual_score_numeric, method = "pearson")
pearson_corr_emd <- cor.test(all_data_clean$emd_test_gan, all_data_clean$visual_score_numeric, method = "pearson")

spearman_corr_fid <- cor.test(all_data_clean$fid, all_data_clean$visual_score_numeric, method = "spearman")
spearman_corr_emd <- cor.test(all_data_clean$emd_test_gan, all_data_clean$visual_score_numeric, method = "spearman")

# Display results
list(
  pearson = list(
    fid = pearson_corr_fid,
    emd = pearson_corr_emd
  ),
  spearman = list(
    fid = spearman_corr_fid,
    emd = spearman_corr_emd
  )
)
```

```{r}
# Linear regression models
model_fid <- lm(visual_score_numeric ~ fid, data = all_data_clean)
model_emd <- lm(visual_score_numeric ~ emd_test_gan, data = all_data_clean)

# Summarize the models
summary(model_fid)
summary(model_emd)
```



# FID SCORE vs generator parameters

```{r}
# Calculate the correlation and test for statistical significance
cor_test_result <- cor.test(all_data$fid, all_data$generator_parameters)

# Extract and print the correlation coefficient
correlation_coefficient <- cor_test_result$estimate
cat("Correlation Coefficient:", correlation_coefficient, "\n")

# Extract and print the p-value
p_value <- cor_test_result$p.value
cat("P-value:", p_value, "\n")
```


```{r}
all_data %>%
 # filter(n_patches==28) %>%
 #filter(n_layers==1) %>%
 # filter(generator_parameters<1000)%>% # remove one outlier
  ggplot(aes(x = generator_parameters, y = fid)) +
   geom_point() +
  geom_smooth(method = "lm", se=TRUE, col = "blue") +
  labs(title = "FID vs number of total parameters",
       subtitle = "All data",
       x = "Generator Parameter",
       y = "FID") +
   scale_shape_discrete(name = "Patch Size") +
  theme_minimal() +
    scale_x_log10() +
  theme(
    plot.title = element_text(size = 18), #face = "bold"
    plot.subtitle = element_text(size = 14),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )
```


# EMD scores vs generator total parameters
```{r}
# Calculate the correlation and test for statistical significance
cor_test_result <- cor.test(all_data$emd_test_gan, all_data$generator_parameters)

# Extract and print the correlation coefficient
correlation_coefficient <- cor_test_result$estimate
cat("Correlation Coefficient:", correlation_coefficient, "\n")

# Extract and print the p-value
p_value <- cor_test_result$p.value
cat("P-value:", p_value, "\n")
```

```{r}
all_data %>%
 # filter(n_patches==28) %>%
 #filter(n_layers==1) %>%
 # filter(generator_parameters<1000)%>% # remove one outlier
  ggplot(aes(x = generator_parameters, y = emd_test_gan)) +
   geom_point() +
  geom_smooth(method = "lm", se=TRUE, col = "blue") +
  labs(title = "EMD vs number of total parameters",
       subtitle = "All data",
       x = "Generator Parameter",
       y = "EMD") +
    scale_x_log10() +
   scale_shape_discrete(name = "Patch Size") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 18), #face = "bold"
    plot.subtitle = element_text(size = 14),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )
```




```{r}
all_data
```


```{r}
# Assuming all_data is your dataframe with columns 'round' and 'FID'
ggplot(all_data, aes(x = factor(round), y = fid)) +
  geom_boxplot() +
  labs(title = "Distribution of FID by Stage",
       subtitle = "All data",
       x = "Round",
       y = "FID") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 18), #face = "bold"
    plot.subtitle = element_text(size = 14),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )
```

```{r}
# Assuming all_data is your dataframe with columns 'round' and 'FID'
ggplot(all_data, aes(x = factor(round), y = emd_test_gan)) +
  geom_boxplot() +
  labs(title = "Distribution of EMD by Stage",
       subtitle = "All data",
       x = "Round",
       y = "EMD") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 18), #face = "bold"
    plot.subtitle = element_text(size = 14),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )
```

