---
title: "R Notebook"
output: html_notebook
---

# The script manipulates and generates plots for the 5th stage of experiments

```{r}
# Importing libraries
library(dplyr)
library(ggplot2)
library(gridExtra)
library(grid)
library(RColorBrewer)
```

## Import the Datasets

```{r}
# Set the main variables:
round <- "final_round5"


base_dir <- "/Volumes/SANDISK32_2"
```


```{r}
# Extract the csv files from the evolutionary directories

data_directory <- file.path(base_dir, round)

csv_files <- list.files(path = data_directory, pattern = "\\.csv$", recursive = TRUE, full.names = TRUE)
csv_files <- csv_files[!grepl("/gan/", csv_files)]
csv_files <- csv_files[!grepl("metadata", csv_files)]
print(csv_files)
```


```{r}
# Folder names and corresponding experiment IDs
folder_experiment_id <- list(
  "24_05_18_16_40_18" = "F_01",
  "24_05_18_17_39_27" = "F_02",
  "24_05_18_21_35_44" = "F_03",
  "24_05_18_21_36_23" = "F_04",
  "24_05_20_09_15_56" = "F_05",
  "24_05_20_09_22_24" = "F_06",
  "24_05_21_21_48_38" = "F_07",
  "24_05_21_21_49_30" = "F_08",
  "24_05_22_08_54_27" = "F_09",
  "24_05_22_08_56_14" = "F_10"
)
```



```{r}
# Function to extract folder name from file path
extract_folder_name <- function(path) {
  parts <- strsplit(path, "/")[[1]]
  return(parts[6])  # Adjust the index based on the actual position of the folder name in your paths
}


# Function to extract folder name from file path
extract_folder_name <- function(path) {
  parts <- strsplit(path, "/")[[1]]
  return(parts[5])  # Adjust the index based on the actual position of the folder name in your paths
}

# Read files into data frames and exclude specified columns
data_frames <- lapply(seq_along(csv_files), function(i) {
  df <- read.csv(csv_files[i]) %>%
    select(-c(Best.Solution, Best.Individual...Start, Best.Individual...End))
  folder_name <- extract_folder_name(csv_files[i])
  experiment_id <- folder_experiment_id[[folder_name]]
  df <- df %>%
    mutate(folder = folder_name, experiment_id = experiment_id)
  assign(paste0("df", i), df, envir = .GlobalEnv)
})
```

Add a column for the number of generations
```{r}
# Function to add a 'generations' column
add_generations <- function(df) {
  df %>%
    mutate(generations = row_number())
}

# Apply the function to each data frame and reassign to the global environment
data_frames <- lapply(seq_along(data_frames), function(i) {
  df <- data_frames[[i]] %>% add_generations()
  assign(paste0("df", i), df, envir = .GlobalEnv)
  return(df)
})

```

## Average number of generations for each experiment
Calculate the average number of generations each experiment ran for, equivalent to the number of rows of each csv file (I verified this, it is indeed equivalent).
```{r}
# List of data frames
data_frame_names <- paste0("df", 1:10)

# Function to get the number of rows for each data frame
num_rows_list <- sapply(data_frame_names, function(df_name) {
  nrow(get(df_name))
})

# Calculate the average number of rows
average_num_rows <- mean(num_rows_list)

# Print the average number of rows
print(paste("The average number of rows is:", average_num_rows))

```

## EMD plots

### Single plot (try-out)

```{r}
# Create the plot for df1
plot_df1 <- ggplot(df1, aes(x = 1:nrow(df1), y = Best.Fitness)) +
  #geom_line(color = "darkblue", size = 1.2) +
  geom_smooth(method = "loess", color = "darkblue", se = FALSE, span = 0.02, size = 1.4) +
  #geom_point(color = "black", size = 0.7, alpha = 0.4) +
  labs(title = "EMD curve for df1", x = "Generations", y = "Best Fitness") 
  #theme_minimal()

# Print the plot
print(plot_df1)
```

### Grid plot
Create a grid plot of all the EMD values for the 10 experiments:

```{r}

# Suppress warnings
options(warn = -1)

# Function to create a plot for each data frame with the experiment ID as the title,
# smaller axis labels, and tilted x-axis labels
create_plot <- function(df) {
  ggplot(df, aes(x = 1:nrow(df), y = Best.Fitness)) +
    geom_line(color = "darkblue", size = 1.2) +
    labs(title = unique(df$experiment_id), x = "Generations", y = "EMD Value") +
    ylim(1.99, 4) +
    theme(axis.title = element_text(size = 8),
          axis.text.x = element_text(angle = 45, hjust = 1),
          plot.title = element_text(size = 12, hjust = 0.5))
}

# List of data frames
data_frames <- list(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10)

# Create a list of plots
plots <- lapply(data_frames, create_plot)

# Arrange the plots in a 2x5 grid with a general title
grid_plot <- grid.arrange(
  grobs = plots,
  ncol = 5,
  nrow = 2,
  top = textGrob("EMD Curves for All Data Frames", gp = gpar(fontsize = 16))

)

# Print the grid plot
suppressMessages(print(grid_plot))
```

### Overlapping plot of all EMDs

```{r}
tail(df1)
```


## Create a plot that shows all 10 EMDs in the same plot.

Find the maximum number of generations across the 10 experiments:
```{r}
max_generations <- max(sapply(data_frames, nrow))
```

Create a new data frame for each experiment with extended generations:
```{r}
extend_generations <- function(df, max_gens) {
  n <- nrow(df)
  extended_df <- df %>%
    right_join(data.frame(generations = 1:max_gens), by = "generations") %>%
    arrange(generations)
  return(extended_df)
}

extended_data_frames <- lapply(data_frames, extend_generations, max_gens = max_generations)
```

Add the experiment_id to each extended data frame and combine them:
```{r}
experiment_labels <- c(
  "1" = "F_01", "2" = "F_02", "3" = "F_03", "4" = "F_04",
  "5" = "F_05", "6" = "F_06", "7" = "F_07", "8" = "F_08",
  "9" = "F_09", "10" = "F_10"
)

combined_data <- bind_rows(extended_data_frames, .id = "experiment_number") %>%
  mutate(experiment_label = factor(experiment_number, labels = experiment_labels))

```

Create and print the plot:
```{r}
emd_plot <- ggplot(combined_data, aes(x = generations, y = Best.Fitness, color = experiment_label)) +
  geom_line(size = 1.2) +
  scale_color_manual(values = scales::hue_pal()(10)) +  # Set pastel colors
  labs(title = "EMD Values for All Experiments", x = "Generations", y = "Best Fitness", color = "Experiment") +
  theme(axis.title = element_text(size = 12),
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, hjust = 0.5))

print(emd_plot)
```

Choose a color blind friendly palette:

```{r}
display.brewer.all(n = 10, colorblindFriendly = TRUE)
```




```{r}
# Define a more subdued color palette
palette <- brewer.pal(n = 10, name = "Paired")

emd_plot <- ggplot(combined_data, aes(x = generations, y = Best.Fitness, color = experiment_label)) +
  geom_line(size = 1.2, alpha = 0.8) +
  scale_color_manual(values = palette) +  # Use subdued color palette
  labs(title = "EMD Values for Stage 5 Experiments", x = "Generations", y = "EMD value", color = "Experiment ID") +
  theme(
    axis.title = element_text(size = 12),
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(size = 16, hjust = 0.5)
  )

suppressMessages(print(emd_plot))

```
















