---
title: "number of gates"
author: "Bianca Massacci"
date: "5/28/2024"
output: html_document
---

This script shows the relationship between the number of patches and the number of qubits and parameters in the *second round* of experiments.


```{r}
# Importing libraries
library(dplyr)
library(ggplot2)
library(tidyr)
```

Create the data frame with the round 2 results

```{r}
data_1 <- data.frame(
  patches = c(1, 1, 1, 2, 2, 2, 7, 7, 7, 14, 14, 14, 28, 28, 28),
  qubits = c(10, 10, 10, 9, 9, 9, 7, 7, 7, 6, 6, 6, 5, 5, 5),
  fid = c(25.01, 25.01, 22.991, 23.074, 23.687, 24.111, 19.517, 19.055, 16.76, 17.478, 3.907, 17.642, 4.687, 20.391, 4.46),
  n_u_gates = c(1, 3, 4, 2, 2, 2, 3, 2, 1, 1, 5, 1, 5, 4, 9),
  n_cx_gates = c(2, 1, 2, 2, 3, 0, 2, 2, 2, 2, 2, 1, 1, 2, 4),
  generator_parameters = c(3, 18, 36, 12, 24, 36, 63, 84, 63, 42, 420, 126, 420, 672, 2268)
)

# View the data
print(data_1)

```

# Number of gates

```{r}
# Create the plot
plot <- ggplot(data_1, aes(x = patches, y = n_u_gates)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.2)) +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Number of U Gates vs Number of Patches",
       x = "Number of Patches",
       y = "Number of U Gates") +
  theme_minimal()

# Display the plot
print(plot)
```



```{r}

summary_data <- data_1 %>%
  group_by(patches) %>%
  summarize(mean_n_u_gates = mean(n_u_gates))

summary_data

# Create the bar plot
plot <- ggplot(summary_data, aes(x = factor(patches), y = mean_n_u_gates)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Mean Number of U Gates by Number of Patches",
       x = "Number of Patches",
       y = "Mean Number of U Gates") +
  theme_minimal()

# Display the plot
print(plot)
```


```{r}

# Create the box plot
plot <- ggplot(data_1, aes(x = factor(patches), y = n_u_gates)) +
  geom_boxplot(fill = "lightblue") +
  labs(title = "Number of U() and CNOT Gates vs Number of Patches",
       subtitle = "Experiment Stage 1",
       x = "Number of Patches",
       y = "Number of U Gates") +
  theme_minimal()

# Display the plot
print(plot)
```


```{r}
# Reshape the data into long format
data_long <- pivot_longer(data_1, cols = c(n_u_gates, n_cx_gates), names_to = "gate_type", values_to = "count")

# Create the box plot with dodged positions
plot <- ggplot(data_long, aes(x = factor(patches), y = count, fill = gate_type)) +
  geom_boxplot(position = position_dodge(0.8), alpha = 0.7) +
  labs(title = "Distribution of U Gates and CX Gates by Number of Patches",
       x = "Number of Patches",
       y = "Count",
       fill = "Gate Type") +
  theme_minimal()

# Display the plot
print(plot)
```


```{r}
# Create the scatter plot with annotations
plot <- ggplot(data_1, aes(x = patches, y = n_u_gates)) +
  geom_point() +
  geom_text(aes(label = n_u_gates), vjust = -1, hjust = 1.2) +
  labs(title = "Number of U Gates vs Number of Patches",
       x = "Number of Patches",
       y = "Number of U Gates") +
  theme_minimal()

# Display the plot
print(plot)
```


```{r}
# Reshape the data into long format
data_long <- pivot_longer(data_1, cols = c(n_u_gates, n_cx_gates), names_to = "gate_type", values_to = "count")

# Create the scatter plot with jitter
plot <- ggplot(data_long, aes(x = factor(patches), y = count, color = gate_type)) +
  geom_jitter(width = 0.2, height = 0.2) +
  labs(title = "Number of U Gates and CX Gates by Number of Patches",
       x = "Number of Patches",
       y = "Count",
       color = "Gate Type") +
  theme_minimal()

# Display the plot
print(plot)
```

```{r}

# Calculate mean and standard deviation for each group
summary_data <- data_1 %>%
  pivot_longer(cols = c(n_u_gates, n_cx_gates), names_to = "gate_type", values_to = "count") %>%
  mutate(gate_type = recode(gate_type, n_u_gates = "U(θ,ϕ,λ)", n_cx_gates = "CNOT")) %>%
  group_by(patches, gate_type) %>%
  summarise(mean_count = mean(count), sd_count = sd(count))

# Create the bar plot with error bars
plot <- ggplot(summary_data, aes(x = factor(patches), y = mean_count, fill = gate_type)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean_count - sd_count, ymax = mean_count + sd_count), 
                position = position_dodge(0.8), width = 0.2) +
  labs(title = "Number of U(θ,ϕ,λ) and CNOT Gates vs Number of Patches",
       subtitle = "Experiment Stage 1",
       x = "Number of Patches",
       y = "Average Count",
       fill = "Gate Type") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 18), #face = "bold"
    plot.subtitle = element_text(size = 14),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )


# Display the plot
print(plot)
```


# Number of parameters
```{r}
data_1
```


```{r}
# Calculate the correlation coefficient
correlation <- cor(data_1$patches, data_1$generator_parameters)
print(paste("Correlation coefficient:", correlation))

# Test the significance of the correlation
correlation_test <- cor.test(data_1$patches, data_1$generator_parameters)
print(correlation_test)
```

The results strongly suggest that there is a significant positive relationship between the number of patches and the total parameters in your data, with a p-value less than 0.05, and  we are also 95% confident that the true correlation coefficient lies between 0.3068 and 0.8954.

```{r}
# Create the plot
plot <- ggplot(data_1, aes(x = patches, y = generator_parameters)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.2)) +
  geom_smooth(method = "lm", se=TRUE, col = "blue") +
  labs(title = "Number of patches vs total generator parameters",
       x = "Patches",
       y = "Generator Parameters") +
  theme_minimal()

# Display the plot
print(plot)
```


# Generator parameters and FID scores

```{r}
# Calculate the correlation coefficient between FID scores and generator parameters
correlation_fid_params <- cor(data_1$fid, data_1$generator_parameters)
print(paste("Correlation coefficient:", correlation_fid_params))

# Test the significance of the correlation
correlation_test_fid_params <- cor.test(data_1$fid, data_1$generator_parameters)
print(correlation_test_fid_params)
```

```{r}
# Create the plot
plot <- ggplot(data_1, aes(x = fid, y = generator_parameters)) +
   geom_point(aes(shape = as.factor(patches)), size = 4, alpha = 0.7, color = "blue", position = position_jitter(width = 0.2, height = 0.2)) +
  geom_smooth(method = "lm", se=TRUE, col = "blue") +
  labs(title = "FID score vs Total Generator Parameters",
       subtitle = "Experiment Stage 1",
       x = "Generator Parameter",
       y = "FID") +
   scale_shape_discrete(name = "Patch Size") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 18), #face = "bold"
    plot.subtitle = element_text(size = 14),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
  )

# Display the plot
print(plot)
```


# Number of patches and FID

```{r}
# Calculate the correlation coefficient
correlation <- cor(data_1$patches, data_1$fid)
print(paste("Correlation coefficient:", correlation))

# Test the significance of the correlation
correlation_test <- cor.test(data_1$patches, data_1$fid)
print(correlation_test)
```

# Number of patches and number of gates


```{r}
# Calculate the correlation coefficient
correlation <- cor(data_1$patches, data_1$n_u_gates)
print(paste("Correlation coefficient:", correlation))

# Test the significance of the correlation
correlation_test <- cor.test(data_1$patches, data_1$n_u_gates)
print(correlation_test)
```

